---
  output: github_document
---

```{r, include=FALSE}
if (requireNamespace("git2r")) {
  repo = git2r::repository(".")
  url = git2r::remote_url(repo, remote = "origin") 
  gh_user = basename(dirname(url))
} else {
  gh_user = "muschellij2"
}
```

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

## Installation

You can install `transcriptr` from GitHub with:

```
# install.packages("remotes")
remotes::install_github("`r gh_user`/transcriptr")
```

## Running the App

```r
shiny::runGitHub("muschellij2/validate_curriculum")
```

## JHU Transcripts

For the necessary input, please visit https://sis.jhu.edu/sswf/, log in and then go to Registration → My Grades, then click [View Unofficial Transcript].  This should download a `Transcript.pdf`.  The `read_jhu_transcript` will read this in and give a `data.frame` of the parsed output.  

The Shiny app: https://jhubiostatistics.shinyapps.io/validate_curriculum/ should also do this for you, allowing you to download a CSV of your data.  If you want the grades, you must check that box for the export.
